\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-20 trunk/europa.tex
update
added some latex markup.

1. EUROPA

@@

1.1 Constraint Programming

@@

CP is normally implemented as part of a programming language and constraints are normally represented as objects [PUG95]. Any constraint can be introduced and, as long as the bounds propagation and domain reduction protocols specified by the host CP system are enforced, it will be indistinguishable from any other ÒprimitiveÓ CP constraint, such as <= or >=.

@@

1.2 EUROPA's Architecture

@@

1.3 Modeling

@@

1.4 Inference

@@

1.5 Search

@@

@@

	1. Unbound Variable: a variable in the partial plan whose domain is not a singleton. Unbound Variables are resolved by specification of a value from the domain of the variable.
	2. Open Condition: an open condition is an inactive token. Inactive tokens can be generated by explicitly posted goals, or when a token is activated, rules may fire that create inactive slave tokens (TODO: point to more detailed decription above in Rules Engine section).
	3. Threat: once a token has been placed in the partial plan it may impact other tokens indirectly through possible overlapping requirements on objects. Recall for example that a token may belong to objects (e.g. Timelines) which require a total order over their tokens. If any 2 tokens could possibly overlap (though not necessarily), then they pose a threat to each other in terms of achieving an extension of the current partial plan which is complete and consistent. Similarly, threats may arise where tokens share a common resource and their current state might yield extensions of the current partial plan which are inconsistent. Threats are resolved by imposing ordering constraints among tokens.

@@

@@

@@

1.6 Future Work?
explain where EUROPA is going? (ANML, incorporation of classical planning algorithms, soft constraints, better search, etc).

The main advantage of CP is the richness of the constraints that can be modeled and the explicit use of logical inference to prune the search space

>>>>

\section{EUROPA}
\label{sec:europa}

@@

\subsection{Constraint Programming}
\label{sec:europa:cp}

@@

CP is normally implemented as part of a programming language and constraints are normally represented as objects [PUG95]. Any constraint can be introduced and, as long as the bounds propagation and domain reduction protocols specified by the host CP system are enforced, it will be indistinguishable from any other “primitive” CP constraint, such as <= or >=.

@@

\subsection{EUROPA's Architecture}
\label{sec:europa:arch}

@@

\subsection{Modeling}
\label{sec:europa:modeling}

@@

\subsection{Inference}
\label{sec:europa:inference}

@@

\subsection{Search}
\label{sec:europa:search}

@@

Given that temporal intervals may extend indefinitely in both positive and negative directions, for problems with a temporal dimension it is also common to specify a Planning Horizon when invoking a solver. The Planning Horizon is the temporal interval that a problem solver has to worry about, any decisions that fall completely outside of the Planning Horizon can be ignored. This is very useful for recurrent activities, consider for instance a model where a medical checkup has to occur every 3 months, the user can model a recurring activity and then use the Planning Horizon to ensure that a finite number of medical checkup activities are generated as part of a plan. This is also useful to ignore activities that may happen too far in the future or in the past to be relevant for a particular plan, this way the user can ensure that the solver is making as few commitments as necessary.

@@

	1. Unbound Variable: a variable in the partial plan whose domain is not a singleton. Unbound Variables are resolved by specification of a value from the domain of the variable.
	2. Open Condition: an open condition is an inactive token. Inactive tokens can be generated by explicitly posted goals, or when a token is activated, rules may fire that create inactive slave tokens (TODO: point to more detailed decription above in Rules Engine section).  Open Conditions can be resolved in three ways: 
		- Merging: A free activity is merged with a matching activity already in the plan. An activity a is said to match an activity a? if a and a? unify and the temporal constraints involving a are satisﬁed by a?. Thus,  a and a? can be considered the same activity and we do not need to introduce a in the plan. Consequently, the compatibilities associated with a are not ﬁred, because they have been already triggered when a? was introduced in the plan. 
		- Activation We introduce a new activity a in the current plan associating it with the proper timeline, but without choosing a speciﬁc time slot for it.The compatibilities associated with a are applied and the subgoal activities resulting from those compatibilities are introduced as free activities. This results in both an ordering ﬂaw, corresponding to the just activated activity, and a number of open condition ﬂaws, corresponding to the new subgoal activities. 
		- Rejection: Some goals may be optional, if that is the case for a particular order condition, its corresponding flaw can be resolved by discarding the inactive token.

	3. Threat: once a token has been placed in the partial plan it may impact other tokens indirectly through possible overlapping requirements on objects. Recall for example that a token may belong to objects (e.g. Timelines) which require a total order over their tokens. If any 2 tokens could possibly overlap (though not necessarily), then they pose a threat to each other in terms of achieving an extension of the current partial plan which is complete and consistent. Similarly, threats may arise where tokens share a common resource and their current state might yield extensions of the current partial plan which are inconsistent. Threats are resolved by imposing ordering constraints among tokens.

@@

\begin{verbatim}

@@

\end{verbatim}

@@
